Strings functions analysis

### 2022-08-24 article.tex
using N, not 10 langs

    A table with the list of different functions from standard string libraries for these languages has been compiled. For the analysis will be selected functions, which are presented at least in three programming languages (out of ten presented). Since for the functions presented only in one-two language, we can conclude that they are used in too special or rare cases. \hl{using N, not 10}

>>>>

    A table with the list of different functions from standard string libraries for these languages has been compiled. For the analysis will be selected functions, which are presented at least in 30 percent of programming languages (out of N presented). Since for the functions presented less than 30 percent language, we can conclude that they are used in too special or rare cases.
